\textbf{Manual Coding Guidelines\\[0.15cm] for Automation Patents}

### 2015-08-20 manual_coding_guidelines/manual_coding_guidelines.tex
Add superscript 1 to fmeasure in table + change name from handbook to guidelines
edit man. coding guideliens

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title {\textbf{Manual Coding Handbook\\[0.15cm]
for Automation Patents}}
\author{
Katja Mann, Lukas P\"uttmann \\  
\textit{University of Bonn}}
\date{\today}

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{\textcolor{myred}{https://www.google.com/patents}}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{\textcolor{myred}{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list.
	\end{itemize}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title {\textbf{Manual Coding Guidelines\\[0.15cm]
for Automation Patents}}
\author{
Katja Mann, Lukas P\"uttmann \\  
\textit{University of Bonn}}
\date{\today}

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{\textcolor{myred}{https://www.google.com/patents}}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{\textcolor{myred}{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface. 
	\item An easy way to reach a patent is to adjust the following url (leave US and replace 6121900 by the patent number):\\[0.1cm]
 \href{https://www.google.de/patents/US6121900}{\texttt{\textcolor{myred}{https://www.google.de/patents/US6121900}}}\\[0.1cm]
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list.
	\end{itemize}
\end{frame}
